Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-17 Manuscript/Manuscript.Rmd
Backbone of intro more or less in shape?

(current, 676 words. Aim for 650)

From what we talked:

1. Disentangling mPFC (unsuccessful meta-analyses)
2. Trouble imaging this area
3. Network stats in the individual as a useful method

The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016). Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007). However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This has prompted the question of whether these distinct phenomena are part of a common underlying brain system, or they can be dissociable.

Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. For example, de la Vega et al. (2016) found subdivisions of mPFC and MCC that are significantly tied to decision making across the literature. In particular, they show that more ventral mPFC regions are increasingly associated with reward and fear. However, they also found that vmPFC coactivates with DMN regions, with no topographical distinction between this network and valuation. Focused work at disentangling DMN from subjective value also failed to separate these systems (Acikalin, Gorgolewski, & Poldrack, 2017). While informative, these meta-analyses relied on peak coordinates derived from group-averaged data. It has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret. Aiming to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks. Gordon et al identify important idiosincrasies in oversampled subjects that are blurred in agglomerative analyses. The trend of individualized analyses has led to finer subdivisions of the DMN (Braga & Buckner, 2018). It is thus possible that the indisitinguishable extent of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.

Given the shortcomings of study-specific and cross-study analyses, there is potential value in combining complementary strengths from both approaches. Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017). A natural next step would be to recruit all possible patterns of covariation within this network. A popular alternative is to rely on graph theoretic methods, which provide a characterization of networks that organically fits brain dynamics (provides an organic avenue to understand brain dynamics?), and thus permits the consideration of the full covariance structure of brain networks.

One great advantage of network science is the ability to characterize connectivity in a way that allows for comparisons among individuals in a meaningful way (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018), thus letting us address the idiosyncrasies mentioned above. In this study, we aim to subdivide mPFC into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making. We address this aim at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; and 2) characterizing the connectivity of all surface vertices for these ROIs.

Do these things truly overlap, or are we not looking close enough?

Add Tor's latest papers to the meta analysis

>>>>

(current, 708 words. Aim for 650)

  The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016). Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007). However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009). Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction (de la Vega et al., 2016). Focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017). These findings highlight multifaceted representations of psychological constructs within mPFC subregions. However, recent activation-based meta-analytic has demonstrated domain specificity in this area (Kragel et al., 2018). In addition, coordinate-based meta-analyses rely on peak coordinates derived from group-averaged data. It has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret. Aiming to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. For example, Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks. Gordon et al identify important idiosincrasies in oversampled subjects that are blurred in agglomerative analyses. Importantly, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018). It is thus possible that the indisitinguishable extent of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present in mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008). As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. A popular approach is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018). Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016). Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018). However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes bipartision through spectral partitioning a more viable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix), and the resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975). This method could thus highlight the cluster of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making. We do this by capitalizing on therespective strengths of meta-analytic and subject-specific analyses of brain data.
